---
title: "2023_04GlucoseTiming"
author: "JarrodLaro"
date: "2025-01-23"
output: html_document
---


```{r}
library(dplyr)
library(ggplot2)
library(VennDiagram)
library(UpSetR)
library(ggvenn)
library(ggpubr)
library(rstatix)
```

______________________________________________________

                Xcalibur Load
                
______________________________________________________


```{r}
MayData <- read.csv("C:/Users/jr144/OneDrive - University of Oklahoma/202513C_Methods_Paper/2023_05GlucoseDosing/2023_05GlucoseDosingFormatted.csv", fileEncoding = 'UTF-8-BOM')

MayDataWithNorm <- MayData %>%
  group_by(Replicate.Name, Molecule) %>%
  mutate(NormalizedArea = Area / sum(Area)) %>%
  ungroup()

MayDataWithNorm <- MayDataWithNorm %>%
  filter(!Dosage %in% c('1mg','5mg'))
```

MayData <- MayData %>%
  filter(Precursor.Adduct %in% c("[M-H]", "[MC13-H]", "[MC213-H]"))
  
MayData <- MayData %>%
  filter(Precursor.Adduct %in% c("[M-H]", "[Max-1-H]", "[Max-H]"))
  
MayData <- MayData %>%
  filter(!Timing %in% c('15min') ) %>%
  filter(!Dosage %in% c('1mg') ) %>%
  filter(Precursor.Adduct %in% c("[M-H]", "[MC13-H]", "[MC213-H]"))
  
MayData <- MayData %>%
  filter(!Timing %in% c('15min') ) %>%
  filter(!Dosage %in% c('1mg') ) %>%
  filter(Precursor.Adduct %in% c("[M-H]", "[Max-1-H]", "[Max-H]"))

MayData <- MayData %>%
  filter(!Timing %in% c('15min') ) %>%
  filter(!Dosage %in% c('1mg') )
__________________________________

12C v 13C
__________________________________

```{r}
AprilData12Cv13C <- MayDataWithNorm %>%
  filter(X12Cv13C %in% c("C12","C13"))

AprilData12Cv13CNonNormalized <- MayDataWithNorm %>%
  filter(X12Cv13C %in% c("C12", "C13")) %>%
  group_by(Replicate.Name, Labeling, Molecule, X12Cv13C) %>%
  summarise(TotalArea = sum(Area), .groups = 'drop')

AprilData12Cv13CNormalized <- MayDataWithNorm %>%
  filter(X12Cv13C %in% c("C12", "C13")) %>%
  group_by(Replicate.Name, Labeling, Molecule, X12Cv13C) %>%
  summarise(TotalArea = sum(NormalizedArea), .groups = 'drop')
```

__________

Non-normalized
__________

```{r}

MoleculeList <- c(unique(AprilData12Cv13CNonNormalized$Molecule))
for (molecule in MoleculeList){
  print(molecule)
  temp <- AprilData12Cv13CNonNormalized[AprilData12Cv13CNonNormalized$Molecule == molecule,]
  
  plot <- ggplot(temp, aes(x = Labeling, y = TotalArea, fill = as.factor(X12Cv13C))) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(position = position_jitterdodge(dodge.width = 0.8, jitter.width = 0.2),
                size = 1, alpha = 0.2) + # Add jittered points
    stat_compare_means(aes(group = X12Cv13C), 
                       method = "wilcox.test", 
                       label = "p.format") +
    labs(
      title = paste0("Boxplot of " , molecule, " Area by LabelStatus"),
      x = "Label Status",
      y = "Area",
      fill = "Label"
    ) +
    theme_minimal()
    print(plot)
}
```

__________

Normalized
__________

```{r}

MoleculeList <- c(unique(AprilData12Cv13CNormalized$Molecule))
for (molecule in MoleculeList){
  print(molecule)
  temp <- AprilData12Cv13CNormalized[AprilData12Cv13CNormalized$Molecule == molecule,]
  
  plot <- ggplot(temp, aes(x = Labeling, y = TotalArea, fill = as.factor(X12Cv13C))) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(position = position_jitterdodge(dodge.width = 0.8, jitter.width = 0.2),
                size = 1, alpha = 0.2) + # Add jittered points
    stat_compare_means(aes(group = X12Cv13C), 
                       method = "wilcox.test", 
                       label = "p.format") +
    labs(
      title = paste0("Boxplot of " , molecule, " Normalized Area by LabelStatus"),
      x = "Label Status",
      y = "Normalized Area",
      fill = "Label"
    ) +
    theme_minimal()
    print(plot)
}
```

__________________________________

Blank Check
__________________________________
```{r}

AprilDataBlankCheckNonNormalized <- MayDataWithNorm %>%
  filter(X12Cv13C %in% c("C13","Blank")) %>%
  group_by(Replicate.Name, Labeling, Molecule, X12Cv13C) %>%
  summarise(TotalArea = sum(Area), .groups = 'drop')

```
__________

Non-normalized
__________

```{r}
MoleculeList <- c(unique(AprilDataBlankCheckNonNormalized$Molecule))
for (molecule in MoleculeList){
  print(molecule)
  temp <- AprilDataBlankCheckNonNormalized[AprilDataBlankCheckNonNormalized$Molecule == molecule,]
  
  plot <- ggplot(temp, aes(x = Labeling, y = TotalArea, fill = as.factor(X12Cv13C))) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(position = position_jitterdodge(dodge.width = 0.8, jitter.width = 0.2),
                size = 1, alpha = 0.2) + # Add jittered points
    stat_compare_means(aes(group = X12Cv13C), 
                       method = "wilcox.test", 
                       label = "p.format") +
    labs(
      title = paste0("Boxplot of " , molecule, " Area by LabelStatus"),
      x = "Label Status",
      y = "Area",
      fill = "Label"
    ) +
    theme_minimal()
    print(plot)
}
```

______________________________________________


   Facial Bleed v Plasma v Blank Unadjusted


______________________________________________

```{r}
MayDataNonnormalizedSum <- MayWithNorm %>%
  filter(!Molecule %in% c('G6P', 'Succinate')) %>%
  group_by(Replicate.Name, Labeling, Molecule, X12Cv13C, Dosage, Organ) %>%
  summarise(TotalArea = sum(Area), .groups = 'drop') %>%
  filter(X12Cv13C %in% c('C13', 'Blank')) %>%
  filter(!Labeling %in% c('Unlabeled')) %>%
  filter(Organ %in% c('FacialBleed', 'Plasma', 'Blank'))
```

```{r}

plot <- ggplot(MayDataNonnormalizedSum, aes(x = Dosage, y = TotalArea, fill = as.factor(Organ))) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(position = position_jitterdodge(dodge.width = 0.8, jitter.width = 0.2),
                size = 1, alpha = 0.2) + # Add jittered points
    stat_compare_means(aes(group = Organ), 
                       method = "wilcox.test", 
                       label = "p.format") +
    labs(
      title = paste0("Boxplot of All Molecules by Normalized Area by LabelStatus"),
      x = "Dosage",
      y = "Normalized Area",
      fill = "Organ"
    ) +
    theme_minimal()
    print(plot)

```
```{r}

MoleculeList <- c(unique(MayDataNonnormalizedSum$Molecule))
for (molecule in MoleculeList){
  print(molecule)
  temp <- MayDataNonnormalizedSum[MayDataNonnormalizedSum$Molecule == molecule,]
  
  plot <- ggplot(temp, aes(x = Dosage, y = TotalArea, fill = as.factor(Organ))) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(position = position_jitterdodge(dodge.width = 0.8, jitter.width = 0.2),
                size = 1, alpha = 0.2) + # Add jittered points
    stat_compare_means(aes(group = Organ), 
                       method = "wilcox.test", 
                       label = "p.format") +
    labs(
      title = paste0("Boxplot of " , molecule, " Normalized Area by LabelStatus"),
      x = "Dosage",
      y = "Normalized Area",
      fill = "Organ"
    ) +
    theme_minimal()
    print(plot)
}
```
______________________________________________


       Facial Bleed v Plasma Normalized


______________________________________________

```{r}
MayDataNormalizedSum <- MayWithNorm %>%
  filter(!Molecule %in% c('G6P', 'Succinate')) %>%
  group_by(Replicate.Name, Labeling, Molecule, X12Cv13C, Dosage, Organ) %>%
  summarise(TotalArea = sum(NormalizedArea), .groups = 'drop') %>%
  filter(X12Cv13C %in% c('C13')) %>%
  filter(!Labeling %in% c('Unlabeled')) %>%
  filter(Organ %in% c('FacialBleed', 'Plasma'))
```

```{r}

plot <- ggplot(MayDataNormalizedSum, aes(x = Dosage, y = TotalArea, fill = as.factor(Organ))) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(position = position_jitterdodge(dodge.width = 0.8, jitter.width = 0.2),
                size = 1, alpha = 0.2) + # Add jittered points
    stat_compare_means(aes(group = Organ), 
                       method = "wilcox.test", 
                       label = "p.format") +
    labs(
      title = paste0("Boxplot of All Molecules by Normalized Area by LabelStatus"),
      x = "Dosage",
      y = "Normalized Area",
      fill = "Organ"
    ) +
    theme_minimal()
    print(plot)

```


```{r}

MoleculeList <- c(unique(MayDataNormalizedSum$Molecule))
for (molecule in MoleculeList){
  print(molecule)
  temp <- MayDataNormalizedSum[MayDataNormalizedSum$Molecule == molecule,]
  
  plot <- ggplot(temp, aes(x = Dosage, y = TotalArea, fill = as.factor(Organ))) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(position = position_jitterdodge(dodge.width = 0.8, jitter.width = 0.2),
                size = 1, alpha = 0.2) + # Add jittered points
    stat_compare_means(aes(group = Organ), 
                       method = "wilcox.test", 
                       label = "p.format") +
    labs(
      title = paste0("Boxplot of " , molecule, " Normalized Area by LabelStatus"),
      x = "Dosage",
      y = "Normalized Area",
      fill = "Organ"
    ) +
    theme_minimal()
    print(plot)
}
```