---
title: "2023_09FastingAndOrganStudy"
author: "JarrodLaro"
date: "2025-01-23"
output: html_document
---


```{r}
library(dplyr)
library(ggplot2)
library(VennDiagram)
library(UpSetR)
library(ggvenn)
library(ggpubr)
library(rstatix)
```

______________________________________________________

                Xcalibur Load
                
______________________________________________________


```{r}
SeptemberData <- read.csv("C:/Users/NewJarrod/OneDrive - University of Oklahoma/202513C_Methods_Paper/2023_09FastingStudy/2023_09FastingStudyFormatted.csv", fileEncoding = 'UTF-8-BOM')

SeptemberData$Organ[SeptemberData$Organ == "UpperHeart"] <- "Heart"
SeptemberData$Organ[SeptemberData$Organ == "RightKidney"] <- "Kidney"
SeptemberData$Organ[SeptemberData$Organ == "RightLiver"] <- "Liver"

SeptemberData$Fasting_Organ <- paste(SeptemberData$FastLength, SeptemberData$Organ, sep = "_")

SeptemberDataWithNorm <- SeptemberData %>%
  group_by(Replicate.Name, Molecule) %>%
  mutate(NormalizedArea = Area / sum(Area)) %>%
  filter(!Organ %in% c("LowerHeart", "LeftKidney", "LeftLiver")) %>%
  ungroup()

```

AprilData <- AprilData %>%
  filter(Precursor.Adduct %in% c("[M-H]", "[MC13-H]", "[MC213-H]"))
  
AprilData <- AprilData %>%
  filter(Precursor.Adduct %in% c("[M-H]", "[Max-1-H]", "[Max-H]"))
  
AprilData <- AprilData %>%
  filter(!Timing %in% c('15min') ) %>%
  filter(!Dosage %in% c('1mg') ) %>%
  filter(Precursor.Adduct %in% c("[M-H]", "[MC13-H]", "[MC213-H]"))
  
AprilData <- AprilData %>%
  filter(!Timing %in% c('15min') ) %>%
  filter(!Dosage %in% c('1mg') ) %>%
  filter(Precursor.Adduct %in% c("[M-H]", "[Max-1-H]", "[Max-H]"))

AprilData <- AprilData %>%
  filter(!Timing %in% c('15min') ) %>%
  filter(!Dosage %in% c('1mg') )
__________________________________

12C v 13C
__________________________________

```{r}
unique(SeptemberDataWithNorm$Organ)

SeptemberData12Cv13CGrouped <- SeptemberDataWithNorm %>%
  filter(X12Cv13C %in% c("C12", "C13")) %>%
  group_by(Replicate.Name, Labeling, Molecule, X12Cv13C) %>%
#  filter(Organ %in% c("UpperHeart")) %>%
  summarise(TotalArea = sum(NormalizedArea), .groups = 'drop')
```


aKG is a little iffy overall, but everything else looks good
-aKG not significant in LeftKidney
-Citrate and the 6Ps iffy but significant in LeftLiver
-All good in LowerHeart
-All good in plasma
-All good in PCo
-aKG and citrate not significant right kidney
-6Ps iffy but significant in RightLiver too. aKG not significant
-All good in upper heart




```{r}

MoleculeList <- c(unique(SeptemberData12Cv13CGrouped$Molecule))
for (molecule in MoleculeList){
  print(molecule)
  temp <- SeptemberData12Cv13CGrouped[SeptemberData12Cv13CGrouped$Molecule == molecule,]
  
  plot <- ggplot(temp, aes(x = Labeling, y = TotalArea, fill = as.factor(X12Cv13C))) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(position = position_jitterdodge(dodge.width = 0.8, jitter.width = 0.2),
                size = 1, alpha = 0.2) + # Add jittered points
    stat_compare_means(aes(group = X12Cv13C), 
                       method = "wilcox.test", 
                       label = "p.format") +
    labs(
      title = paste0("Boxplot of " , molecule, " Normalized Area by LabelStatus"),
      x = "Label Status",
      y = "Normalized Area",
      fill = "Label"
    ) +
    theme_minimal()
    print(plot)
}
```
__________________________________

Heart Comparison
__________________________________

```{r}
SeptemberDataHeartSamples <- SeptemberDataWithNorm %>%
  filter(X12Cv13C %in% c("C13")) %>%
  filter(!Labeling %in% c('Unlabeled')) %>%
  group_by(Replicate.Name, Labeling, Molecule, X12Cv13C, Organ) %>%
  filter(Organ %in% c("UpperHeart", "LowerHeart")) %>%
  summarise(TotalArea = sum(NormalizedArea), .groups = 'drop')
```

No significant differences, but aconitate and citrate get close




```{r}

MoleculeList <- c(unique(SeptemberDataHeartSamples$Molecule))
for (molecule in MoleculeList){
  print(molecule)
  temp <- SeptemberDataHeartSamples[SeptemberDataHeartSamples$Molecule == molecule,]
  
  plot <- ggplot(temp, aes(x = Organ, y = TotalArea, fill = as.factor(X12Cv13C))) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(position = position_jitterdodge(dodge.width = 0.8, jitter.width = 0.2),
                size = 1, alpha = 0.2) + # Add jittered points
    stat_compare_means(aes(group = Organ), 
                       method = "wilcox.test", 
                       label = "p.format") +
    labs(
      title = paste0("Boxplot of " , molecule, " Normalized Area by LabelStatus"),
      x = "Label Status",
      y = "Normalized Area",
      fill = "Label"
    ) +
    theme_minimal()
    print(plot)
}
```


__________________________________

Liver Comparison
__________________________________

```{r}
SeptemberDataLiverSamples <- SeptemberDataWithNorm %>%
  filter(X12Cv13C %in% c("C13")) %>%
  filter(!Labeling %in% c('Unlabeled')) %>%
  group_by(Replicate.Name, Labeling, Molecule, X12Cv13C, Organ) %>%
  filter(Organ %in% c("LeftLiver", "RightLiver")) %>%
  summarise(TotalArea = sum(NormalizedArea), .groups = 'drop')
```

Citrate is significant, everything else is fine




```{r}

MoleculeList <- c(unique(SeptemberDataLiverSamples$Molecule))
for (molecule in MoleculeList){
  print(molecule)
  temp <- SeptemberDataLiverSamples[SeptemberDataLiverSamples$Molecule == molecule,]
  
  plot <- ggplot(temp, aes(x = Organ, y = TotalArea, fill = as.factor(X12Cv13C))) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(position = position_jitterdodge(dodge.width = 0.8, jitter.width = 0.2),
                size = 1, alpha = 0.2) + # Add jittered points
    stat_compare_means(aes(group = Organ), 
                       method = "wilcox.test", 
                       label = "p.format") +
    labs(
      title = paste0("Boxplot of " , molecule, " Normalized Area by LabelStatus"),
      x = "Label Status",
      y = "Normalized Area",
      fill = "Label"
    ) +
    theme_minimal()
    print(plot)
}
```

__________________________________

Kidney Comparison
__________________________________

```{r}
SeptemberDataKidneySamples <- SeptemberDataWithNorm %>%
  filter(X12Cv13C %in% c("C13")) %>%
  filter(!Labeling %in% c('Unlabeled')) %>%
  group_by(Replicate.Name, Labeling, Molecule, X12Cv13C, Organ) %>%
  filter(Organ %in% c("LeftKidney", "RightKidney")) %>%
  summarise(TotalArea = sum(NormalizedArea), .groups = 'drop')
```

All the same

```{r}

MoleculeList <- c(unique(SeptemberDataKidneySamples$Molecule))
for (molecule in MoleculeList){
  print(molecule)
  temp <- SeptemberDataKidneySamples[SeptemberDataKidneySamples$Molecule == molecule,]
  
  plot <- ggplot(temp, aes(x = Organ, y = TotalArea, fill = as.factor(X12Cv13C))) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(position = position_jitterdodge(dodge.width = 0.8, jitter.width = 0.2),
                size = 1, alpha = 0.2) + # Add jittered points
    stat_compare_means(aes(group = Organ), 
                       method = "wilcox.test", 
                       label = "p.format") +
    labs(
      title = paste0("Boxplot of " , molecule, " Normalized Area by LabelStatus"),
      x = "Label Status",
      y = "Normalized Area",
      fill = "Label"
    ) +
    theme_minimal()
    print(plot)
}
```


__________________________________

Blank Check
__________________________________

All molecules are better than blank overall


```{r}

AprilDataBlankCheckNonNormalized <- AprilDataWithNorm %>%
  filter(X12Cv13C %in% c("Blank")) %>%
  group_by(Replicate.Name, Labeling, Molecule, X12Cv13C) %>%
  summarise(TotalArea = sum(Area), .groups = 'drop')

SeptemberData13CGroupedNonNormalized <- SeptemberDataWithNorm %>%
  filter(X12Cv13C %in% c("C13")) %>%
  group_by(Replicate.Name, Labeling, Molecule, X12Cv13C) %>%
#  filter(Organ %in% c("UpperHeart")) %>%
  summarise(TotalArea = sum(Area), .groups = 'drop')

BlankCheck <- rbind(AprilDataBlankCheckNonNormalized, SeptemberData13CGroupedNonNormalized)
```
__________

Non-normalized
__________

```{r}
MoleculeList <- c(unique(BlankCheck$Molecule))
for (molecule in MoleculeList){
  print(molecule)
  temp <- BlankCheck[BlankCheck$Molecule == molecule,]
  
  plot <- ggplot(temp, aes(x = Labeling, y = TotalArea, fill = as.factor(X12Cv13C))) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(position = position_jitterdodge(dodge.width = 0.8, jitter.width = 0.2),
                size = 1, alpha = 0.2) + # Add jittered points
    stat_compare_means(aes(group = X12Cv13C), 
                       method = "wilcox.test", 
                       label = "p.format") +
    labs(
      title = paste0("Boxplot of " , molecule, " Area by LabelStatus"),
      x = "Label Status",
      y = "Area",
      fill = "Label"
    ) +
    theme_minimal()
    print(plot)
}
```
______________________________________________


            Fasting analysis by Molecule


______________________________________________

Compare samples between Cohorts

```{r}
SeptemberDataFastingComparison <- SeptemberDataWithNorm %>%
#  filter(!Molecule %in% c('aKG', 'Citrate')) %>%
  group_by(Replicate.Name, Labeling, Molecule, X12Cv13C, FastLength, Organ, Fasting_Organ) %>%
  summarise(TotalArea = sum(NormalizedArea), .groups = 'drop') %>%
  filter(X12Cv13C %in% c('C13')) %>%
  filter(!Labeling %in% c('Unlabeled'))

p_value_results <- data.frame(
  Molecule = character(),
  Organ = character(),
  Test = character(),
  P_Value = numeric(),
  stringsAsFactors = FALSE
)

for (molecule in unique(SeptemberDataFastingComparison$Molecule)) {
  for (organ in unique(SeptemberDataFastingComparison$Organ)) {
    
    # Extract TotalArea values for both fasting lengths
    total_area_90 <- SeptemberDataFastingComparison[
      SeptemberDataFastingComparison$Molecule == molecule & 
      SeptemberDataFastingComparison$Organ == organ & 
      SeptemberDataFastingComparison$FastLength == "90Minutes", ]$TotalArea
    
    total_area_270 <- SeptemberDataFastingComparison[
      SeptemberDataFastingComparison$Molecule == molecule & 
      SeptemberDataFastingComparison$Organ == organ & 
      SeptemberDataFastingComparison$FastLength == "270Minutes", ]$TotalArea
    
    # Perform Shapiro-Wilk normality test
    normalcy90 <- shapiro.test(total_area_90)$p.value
    normalcy270 <- shapiro.test(total_area_270)$p.value
    
    # Choose the appropriate test based on normality
    if (normalcy90 < 0.05 | normalcy270 < 0.05) {
      test_used <- "Wilcoxon"
      p_val <- wilcox.test(total_area_90, total_area_270)$p.value
    } else {
      test_used <- "T-test"
      p_val <- t.test(total_area_90, total_area_270)$p.value
    }
    
    # Append results to the dataframe
    p_value_results <- rbind(p_value_results, data.frame(
      Molecule = molecule,
      Organ = organ,
      Test = test_used,
      P_Value = p_val,
      stringsAsFactors = FALSE
    ))
  }
}

# Print the final dataframe with results
print(p_value_results)

write.csv(p_value_results, "MoleculePVals.csv")
```

```{r}
theme_custom <- theme(text = element_text(size = 12),
                      panel.grid = element_blank(),
                      panel.grid.major.y = element_line(colour = "#8f8d8d", linetype = 2),
                      panel.grid.minor.y = element_line(colour = "#8f8d8d", linetype = 2),
                      plot.title.position = 'plot',
                      legend.position = 'top',
)

plot <- ggplot(SeptemberDataFastingComparison, aes(x = Organ, y = TotalArea, fill = as.factor(FastLength))) +
    geom_boxplot(outlier.shape = NA, position = position_dodge(width = 0.75)) +  # Dodge boxplots by X12Cv13C
    geom_jitter(aes(color = as.factor(Molecule), group = FastLength),  # Ensure proper grouping
                position = position_jitterdodge(dodge.width = 0.75, jitter.width = 0.2),  
                size = 1, 
                alpha = 0.5) +
    stat_compare_means(aes(group = FastLength), 
                       method = "wilcox.test", 
                       label = "p.format",
                       size = 5) +
    labs(
      x = "Organ",
      y = "Normalized Area",
      color = "Molecule"
    ) +
  theme_set(theme_bw() + theme_custom) +
  ylim(0,1.05) +
  scale_color_brewer(palette = "Dark2") +  
  scale_fill_brewer(palette = "Pastel1") +
  #guides(fill = "none",color = guide_legend(title = "Molecule"),X12Cv13C = "none")  +
  theme(
    axis.title = element_text(size = 14),       # Size for axis titles
    axis.text = element_text(size = 14),        # Size for axis labels

    legend.text = element_text(size = 16)       # Size for legend labels
  )

plot(plot)
```

```{r}
MoleculeList <- c(unique(SeptemberDataFastingComparison$Molecule))
for (molecule in MoleculeList){
  print(molecule)
  temp <- SeptemberDataFastingComparison[SeptemberDataFastingComparison$Molecule == molecule,]
  

  plot <- ggplot(temp, aes(x = Organ, y = TotalArea, fill = as.factor(FastLength))) +
      geom_boxplot(outlier.shape = NA, position = position_dodge(width = 0.75)) +  # Dodge boxplots by X12Cv13C
      geom_jitter(aes(color = as.factor(Molecule), group = FastLength),  # Ensure proper grouping
                  position = position_jitterdodge(dodge.width = 0.75, jitter.width = 0.2),  
                  size = 1, 
                  alpha = 0.5) +
      stat_compare_means(aes(group = FastLength), 
                         method = "t.test", 
                         label = "p.format",
                         size = 5) +
      labs(
        x = "Organ",
        y = "Normalized Area",
        color = "Molecule"
      ) +
    theme_set(theme_bw() + theme_custom) +
    ylim(0,1.05) +
    scale_color_brewer(palette = "Dark2") +  
    scale_fill_brewer(palette = "Pastel1") +
    #guides(fill = "none",color = guide_legend(title = "Molecule"),X12Cv13C = "none")  +
    theme(
      axis.title = element_text(size = 14),       # Size for axis titles
      axis.text = element_text(size = 14),        # Size for axis labels
      legend.text = element_text(size = 16)       # Size for legend labels
    )
  print(plot)
}
```


______________________________________________


          Fasting analysis by Organ


______________________________________________

Compare samples between Cohorts

```{r}
SeptemberDataFastingComparison <- SeptemberDataWithNorm %>%
#  filter(!Molecule %in% c('aKG', 'Citrate')) %>%
  group_by(Replicate.Name, Labeling, Molecule, X12Cv13C, FastLength, Organ, Fasting_Organ) %>%
  summarise(TotalArea = sum(NormalizedArea), .groups = 'drop') %>%
  filter(X12Cv13C %in% c('C13')) %>%
  filter(!Labeling %in% c('Unlabeled')) %>%
  filter(Organ %in% c("Heart"))
```


```{r}
theme_custom <- theme(text = element_text(size = 12),
                      panel.grid = element_blank(),
                      panel.grid.major.y = element_line(colour = "#8f8d8d", linetype = 2),
                      panel.grid.minor.y = element_line(colour = "#8f8d8d", linetype = 2),
                      plot.title.position = 'plot',
                      legend.position = 'top',
)

plot <- ggplot(SeptemberDataFastingComparison, aes(x = Molecule, y = TotalArea, fill = factor(FastLength,levels = c("90Minutes", "270Minutes")))) +
    geom_boxplot(outlier.shape = NA, position = position_dodge(width = 0.75)) +  # Dodge boxplots by X12Cv13C
    geom_jitter(aes(x = Molecule, group = factor(FastLength,levels = c("90Minutes", "270Minutes"))),  # Ensure proper grouping
                position = position_jitterdodge(dodge.width = 0.75, jitter.width = 0.2),  
                size = 1, 
                alpha = 0.5) +
    #stat_compare_means(aes(group = FastLength), method = "wilcox.test", label = "p.format", size = 5) +
    labs(
      x = "Organ",
      y = "Labeled Fraction",
      color = "Molecule"
    ) +
  theme_set(theme_bw() + theme_custom) +
  ylim(0,1.05) +
  scale_color_brewer(palette = "Dark2") +  
  scale_fill_manual(values = c('#90EE90', "#FF77FF")) +
  guides(fill = "none",color = guide_legend(title = "Molecule"),X12Cv13C = "none")  +
  theme(
    axis.title = element_text(size = 14),       # Size for axis titles
    axis.text = element_text(size = 18),        # Size for axis labels
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),  # Hides x-axis label
    axis.title.y = element_text(size = 24),  
    legend.position = "none"  
  )

plot(plot)

SeptemberDataFastingComparison %>%
    group_by(Molecule) %>%
    summarise(
      Area_90 = median(TotalArea[FastLength == "90Minutes"], na.rm = TRUE),
      Area_270 = median(TotalArea[FastLength == "270Minutes"], na.rm = TRUE),
      Ratio = ifelse(Area_270 != 0, Area_90 / Area_270, NA)
    )

ggsave("CombinedHeartFastLength.png",
       width = 10,
       height = 7,
       units = "in",
       dpi = 600)

```

```{r}
OrganList <- c(unique(SeptemberDataFastingComparison$Organ))
for (organ in OrganList){
  print(organ)
  temp <- SeptemberDataFastingComparison[SeptemberDataFastingComparison$Organ == organ,]
  
  print(paste0("13C plasma p-value ", shapiro.test(AprilMayTimingOrgan[AprilMayTimingOrgan$Dosage_Organ == "1mg_Plasma",]$TotalArea)$p.value))

  plot <- ggplot(temp, aes(x = Molecule, y = TotalArea, fill = as.factor(FastLength))) +
      geom_boxplot(outlier.shape = NA, position = position_dodge(width = 0.75)) +  # Dodge boxplots by X12Cv13C
      geom_jitter(aes(color = as.factor(Organ), group = FastLength),  # Ensure proper grouping
                  position = position_jitterdodge(dodge.width = 0.75, jitter.width = 0.2),  
                  size = 1, 
                  alpha = 0.5) +
      stat_compare_means(aes(group = FastLength), 
                         method = "wilcox.test", 
                         label = "p.format",
                         size = 5) +
      labs(
        x = "Organ",
        y = "Normalized Area",
        color = "Molecule"
      ) +
    theme_set(theme_bw() + theme_custom) +
    ylim(0,1.05) +
    scale_color_brewer(palette = "Dark2") +  
    scale_fill_brewer(palette = "Pastel1") +
    #guides(fill = "none",color = guide_legend(title = "Molecule"),X12Cv13C = "none")  +
    theme(
      axis.title = element_text(size = 14),       # Size for axis titles
      axis.text = element_text(size = 14),        # Size for axis labels
      legend.text = element_text(size = 16)       # Size for legend labels
    )
  print(plot)
}
```








Compare samples between Cohorts

```{r}
SeptemberDataFastingComparison <- SeptemberDataWithNorm %>%
#  filter(!Molecule %in% c('aKG', 'Citrate')) %>%
  group_by(Replicate.Name, Labeling, Molecule, X12Cv13C, FastLength, Organ, Fasting_Organ) %>%
  summarise(TotalArea = sum(NormalizedArea), .groups = 'drop') %>%
  filter(X12Cv13C %in% c('C13')) %>%
  filter(!Labeling %in% c('Unlabeled')) %>%
  filter(Organ %in% c("Liver"))
```


```{r}
theme_custom <- theme(text = element_text(size = 12),
                      panel.grid = element_blank(),
                      panel.grid.major.y = element_line(colour = "#8f8d8d", linetype = 2),
                      panel.grid.minor.y = element_line(colour = "#8f8d8d", linetype = 2),
                      plot.title.position = 'plot',
                      legend.position = 'top',
)

plot <- ggplot(SeptemberDataFastingComparison, aes(x = Molecule, y = TotalArea, fill = factor(FastLength,levels = c("90Minutes", "270Minutes")))) +
    geom_boxplot(outlier.shape = NA, position = position_dodge(width = 0.75)) +  # Dodge boxplots by X12Cv13C
    geom_jitter(aes(x = Molecule, group = factor(FastLength,levels = c("90Minutes", "270Minutes"))),  # Ensure proper grouping
                position = position_jitterdodge(dodge.width = 0.75, jitter.width = 0.2),  
                size = 1, 
                alpha = 0.5) +
    #stat_compare_means(aes(group = FastLength), method = "wilcox.test", label = "p.format", size = 5) +
    labs(
      x = "Organ",
      y = "Labeled Fraction",
      color = "Molecule"
    ) +
  theme_set(theme_bw() + theme_custom) +
  ylim(0,1.05) +
  scale_color_brewer(palette = "Dark2") +  
  scale_fill_manual(values = c('#90EE90', "#FF77FF")) +
  guides(fill = "none",color = guide_legend(title = "Molecule"),X12Cv13C = "none")  +
  theme(
    axis.title = element_text(size = 14),       # Size for axis titles
    axis.text = element_text(size = 18),        # Size for axis labels
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),  # Hides x-axis label
    axis.title.y = element_text(size = 24),  
    legend.position = "none"  
  )

plot(plot)

SeptemberDataFastingComparison %>%
    group_by(Molecule) %>%
    summarise(
      Area_90 = median(TotalArea[FastLength == "90Minutes"], na.rm = TRUE),
      Area_270 = median(TotalArea[FastLength == "270Minutes"], na.rm = TRUE),
      Ratio = ifelse(Area_270 != 0, Area_90 / Area_270, NA)
    )

ggsave("CombinedLiverFastLength.png",
       width = 10,
       height = 7,
       units = "in",
       dpi = 600)

```




